# Results
## Import Library and Dataset
```r
library(dplyr)
library(tidyverse)
library(plotly)
library(ggplot2)
library(treemap)

df_population <- read.csv("Datasets/cleaned/df_population.csv")
df_continent <- read.csv("Datasets/cleaned/continent.csv")
tb_cleaning <- read.csv("Datasets/cleaned/df_tb_cleaning_2.csv")
tb_original <- read.csv("Datasets/cleaned/tb_cleaning.csv")
tb_population_geo <- read.csv("Datasets/cleaned/tb_population_geo.csv")
vaccine_cleaned <- read.csv("Datasets/cleaned/vaccine_cleaned.csv")
vaccine_pivoted <- read.csv("Datasets/cleaned/vaccine_pivoted.csv")

```
```{r}
library(dplyr)
library(tidyverse)
library(plotly)
library(ggplot2)
library(treemap)

df_population <- read.csv("Datasets/cleaned/df_population.csv")
df_continent <- read.csv("Datasets/cleaned/continent.csv")
tb_cleaning <- read.csv("Datasets/cleaned/df_tb_cleaning_2.csv")
tb_original <- read.csv("Datasets/cleaned/tb_cleaning.csv")
tb_population_geo <- read.csv("Datasets/cleaned/tb_population_geo.csv")
vaccine_cleaned <- read.csv("Datasets/cleaned/vaccine_cleaned.csv")
vaccine_pivoted <- read.csv("Datasets/cleaned/vaccine_pivoted.csv")
vaccine_population_geo <- read.csv("Datasets/cleaned/vaccine_population_geo.csv")
```

## Merge Vaccine Data with TB Data
```r
new_incidence <- tb_population_geo %>% select(2,4,10)
vaccine_inc <- merge(new_incidence,vaccine_population_geo,by=c('iso3','year'))
tb_rate <- tb_cleaning %>% select(2:3,28)
vaccine_tb_rate <- merge(tb_rate, vaccine_inc, by=c('iso3','year'))
head(vaccine_tb_rate)
```

```{r}
new_incidence <- tb_population_geo %>% select(iso3,year,c_newinc)
vaccine_inc <- merge(new_incidence,vaccine_population_geo,by=c('iso3','year'))
tb_rate <- tb_cleaning %>% select(iso3,year,tb_infection_rate)
vaccine_tb_rate <- merge(tb_rate, vaccine_inc, by=c('iso3','year'))
head(vaccine_tb_rate)
```


## TB Positive Cases From 1980 - 2021
* The positive TB cases worldwids has a generally increasing trend from 1980 to 2021 and we assume the reason for is trend is the steady increase of the wold population. Also, we notice that there was a drop in 2020 and covid-19 might be one of the main reasons. 
```r
sum_year <- tb_original %>%
            group_by(year) %>%
            summarize(total_positive = sum(c_newinc))
fig1 <- plot_ly(sum_year, x = ~year, y = ~total_positive, 
                type = 'scatter', mode = 'lines+markers', 
                fill = 'tozeroy', name = 'Positive TB Cases') %>% 
        layout(
          xaxis = list(range=c(1979,2022)),
          plot_bgcolor='#BBBBBB',
          yaxis = list(title='Total Positive'))


temp_df <- df_population %>% 
     group_by(year) %>% 
     replace(is.na(.), 0) %>% 
     summarize(popultion_sum = sum(population))
fig2 <- plot_ly(temp_df, x = ~year, y = ~popultion_sum, 
                type = 'scatter', mode = 'lines+markers', 
                name = 'World Population') %>% 
        layout(
          xaxis = list(range=c(1979,2022)),
          plot_bgcolor='#BBBBBB',
          yaxis = list(title='Total Positive'),
          title = 'Total Positive Test(1980-2021)')

fig <- subplot(fig1, fig2, nrows = 2) %>% 
       layout(title = 'Total Positive Test and World Population (1980-2021)')

fig
```


```{r}
sum_year <- tb_original %>%
            group_by(year) %>%
            summarize(total_positive = sum(c_newinc))
fig1 <- plot_ly(sum_year, x = ~year, y = ~total_positive, 
                type = 'scatter', mode = 'lines+markers', 
                fill = 'tozeroy', name = 'Positive TB Cases') %>% 
        layout(
          xaxis = list(range=c(1979,2022)),
          plot_bgcolor='#BBBBBB',
          yaxis = list(title='Total Positive'))


temp_df <- df_population %>% 
     group_by(year) %>% 
     replace(is.na(.), 0) %>% 
     summarize(popultion_sum = sum(population))
fig2 <- plot_ly(temp_df, x = ~year, y = ~popultion_sum, 
                type = 'scatter', mode = 'lines+markers', 
                name = 'World Population') %>% 
        layout(
          xaxis = list(range=c(1979,2022)),
          plot_bgcolor='#BBBBBB',
          yaxis = list(title='Total Positive'),
          title = 'Total Positive Test(1980-2021)')

fig <- subplot(fig1, fig2, nrows = 2) %>% 
       layout(title = 'Total Positive Test and World Population (1980-2021)')

fig
```
## TB Cases by Continents From 1992-2019
* Asia has the highest number of TB cases among 5 continents and Africa takes the second. And the number of cases in Americas and Europe do not change a lot from 1980 to 2021.
```
p <- ggplot(vaccine_tb_rate, aes(x=year, weight = c_newinc, color=continent, fill = continent)) +
  geom_histogram(binwidth=1) +
  ylab("Sum of TB cases")
fig <- ggplotly(p)
fig
```

```{r}
p <- ggplot(vaccine_tb_rate, aes(x=year, weight = c_newinc, color=continent, fill = continent)) +
  geom_histogram(binwidth=1) +
  ylab("Sum of TB Cases") +
  scale_fill_brewer(palette = "Spectral") + 
  ggtitle("TB Cases by Continent(1992-2019)")
fig <- ggplotly(p)
fig

```
## Infection Rate by Continent
* Oceania has the highest variance because it contains the least population. Besides Oceania, Africa has the highest TB infection rate. Also among the years, TB infection rate of Europe and Americas decreases while that of Africa and Asia fluctuate.
```r 
fig <- plot_ly(data=vaccine_tb_rate, x = ~tb_infection_rate, y=~continent,frame = ~year, type='box',color=~continent)
fig %>% layout(
  title = "Infection Rate by Continent",
  xaxis = list(title='Continent')
)
```

```{r}
fig1 <- plot_ly(data=vaccine_tb_rate, x = ~tb_infection_rate, y=~continent, 
               frame = ~year, type='box',
               color=~continent, colors = 'Spectral') %>% 
  layout(
    plot_bgcolor='#BBBBBB',
    title = "Infection Rate by Continent",
    xaxis = list(title='Continent'))

fig1
```

* This graph is used to help understand the graph above, however, due to the tech limit, we can not put two graphs with different plotting method together.
```r
temp_df <- df_population %>% 
           filter(year == 2019) %>% 
           group_by(iso3) %>%
           summarize(popultion = sum(population))

temp_df <- merge(df_continent, temp_df, by = 'iso3') %>% 
           select(iso3, continent, popultion)
fig2 <- treemap(temp_df, 
        index=c("continent","iso3"),
        vSize = "popultion",
        vColor = "popultion",
        type='value',
        palette = 'Spectral',
        title = 'Population Distribution in 2019')
```

```{r}
temp_df <- df_population %>% 
           filter(year == 2019) %>% 
           group_by(iso3) %>%
           summarize(popultion = sum(population))

temp_df <- merge(df_continent, temp_df, by = 'iso3') %>% 
           select(iso3, continent, popultion)
fig2 <- treemap(temp_df, 
        index=c("continent","iso3"),
        vSize = "popultion",
        vColor = "popultion",
        type='value',
        palette = 'Spectral',
        title = 'Population Distribution in 2019')
```

## Age and Gender Plots
* For female, people between 25 to 44 have a higher chance being infected TB and the that of male seems uniform for all ages except 0-14. Generally, people under 14 and over 65 has a lower chance being infected. The possible reason is people usually take the vaccination during infancy period and the protection from TB vaccination usually last for 2 years. 
```r
age_graph <- tb_cleaning %>%
            select(iso3, year, continent, new_sp_m014, new_sp_m1524, new_sp_m2534, new_sp_m3544, 
                   new_sp_m4554, new_sp_m5564, new_sp_m65, new_sp_f014, new_sp_f1524, new_sp_f2534, 
                   new_sp_f3544, new_sp_f4554, new_sp_f5564, new_sp_f65) %>%
            replace(is.na(.), 0) %>%
            group_by(year, continent) %>%
            summarize_if(is.numeric, sum) %>%
            filter(year == 2019) %>%
            rename(male_0to14 = new_sp_m014,
                   male_15to24 = new_sp_m1524,
                   male_25to34 = new_sp_m2534,
                   male_35to44 = new_sp_m3544,
                   male_45to54 = new_sp_m4554,
                   male_55to64 = new_sp_m5564,
                   male_65 = new_sp_m65,
                   female_0to14 = new_sp_f014,
                   female_15to24 = new_sp_f1524,
                   female_25to34 = new_sp_f2534,
                   female_35to44 = new_sp_f3544,
                   female_45to54 = new_sp_f4554,
                   female_55to24 = new_sp_f5564,
                   female_65 = new_sp_f65) %>%
            pivot_longer(cols = -c("year", "continent"),
                         names_to = c('gender', 'age'),
                         names_sep = "_",
                         values_to = 'Freq')
g1 <- age_graph %>%
    ggplot(aes(fill = age, y = continent, x = Freq)) + 
    geom_bar(position = "fill", stat = "identity", show.legend = FALSE) +
    facet_grid(gender~., scales = "free_y", space = "free_y") +
    scale_fill_brewer(palette = "Spectral") + 
    theme(axis.text.x = element_text(angle = 30, vjust = 1, hjust=1))

g2 <- age_graph %>%
      group_by(age, gender) %>%
      summarize(sum = sum(Freq), .groups = 'drop') %>%
      filter(gender == 'male') %>%
      ggplot(aes(x = age, y = sum, fill = age)) +
      geom_bar(stat = "identity") +
      scale_fill_brewer(palette = "Spectral") +
      ggtitle("Male TB Patient among ages") + 
      theme(axis.text.x = element_text(angle = 30, vjust = 1, hjust=1))

g3 <- age_graph %>% 
      group_by(age, gender) %>% 
      summarize(sum = sum(Freq), .groups = 'drop') %>% 
      filter(gender == 'female') %>% 
      ggplot(aes(x = age, y = sum, fill = age)) +
      geom_bar(stat = "identity", show.legend = FALSE) + 
      scale_fill_brewer(palette = "Spectral") +
      ggtitle("Female TB Patient among ages") + 
      theme(axis.text.x = element_text(angle = 30, vjust = 1, hjust=1))

(g2|g3)/g1
```

```{r}
age_graph <- tb_cleaning %>%
            select(iso3, year, continent, new_sp_m014, new_sp_m1524, new_sp_m2534, new_sp_m3544, 
                   new_sp_m4554, new_sp_m5564, new_sp_m65, new_sp_f014, new_sp_f1524, new_sp_f2534, 
                   new_sp_f3544, new_sp_f4554, new_sp_f5564, new_sp_f65) %>%
            replace(is.na(.), 0) %>%
            group_by(year, continent) %>%
            summarize_if(is.numeric, sum) %>%
            filter(year == 2019) %>%
            rename(male_0to14 = new_sp_m014,
                   male_15to24 = new_sp_m1524,
                   male_25to34 = new_sp_m2534,
                   male_35to44 = new_sp_m3544,
                   male_45to54 = new_sp_m4554,
                   male_55to64 = new_sp_m5564,
                   male_65 = new_sp_m65,
                   female_0to14 = new_sp_f014,
                   female_15to24 = new_sp_f1524,
                   female_25to34 = new_sp_f2534,
                   female_35to44 = new_sp_f3544,
                   female_45to54 = new_sp_f4554,
                   female_55to24 = new_sp_f5564,
                   female_65 = new_sp_f65) %>%
            pivot_longer(cols = -c("year", "continent"),
                         names_to = c('gender', 'age'),
                         names_sep = "_",
                         values_to = 'Freq')
```

```{r, fig.height=5}
g1 <- age_graph %>%
    ggplot(aes(fill = age, y = continent, x = Freq)) + 
    geom_bar(position = "fill", stat = "identity", show.legend = FALSE) +
    facet_grid(gender~., scales = "free_y", space = "free_y") +
    scale_fill_brewer(palette = "Spectral") + 
    theme(axis.text.x = element_text(angle = 30, vjust = 1, hjust=1))

g2 <- age_graph %>%
      group_by(age, gender) %>%
      summarize(sum = sum(Freq), .groups = 'drop') %>%
      filter(gender == 'male') %>%
      ggplot(aes(x = age, y = sum, fill = age)) +
      geom_bar(stat = "identity") +
      scale_fill_brewer(palette = "Spectral") +
      ggtitle("Male TB Patient among ages") + 
      theme(axis.text.x = element_text(angle = 30, vjust = 1, hjust=1))

g3 <- age_graph %>% 
      group_by(age, gender) %>% 
      summarize(sum = sum(Freq), .groups = 'drop') %>% 
      filter(gender == 'female') %>% 
      ggplot(aes(x = age, y = sum, fill = age)) +
      geom_bar(stat = "identity", show.legend = FALSE) + 
      scale_fill_brewer(palette = "Spectral") +
      ggtitle("Female TB Patient among ages") + 
      theme(axis.text.x = element_text(angle = 30, vjust = 1, hjust=1))

(g2|g3)/g1
```



## TB Incident Among HIV and Non-HIV Patients
* We can clearly see that HIV patients has a higher rate infected by TB and this pattern is especially obvious in Asia.
```r
hiv_graph <- tb_cleaning %>%
            select(iso3, year, continent, country, hiv_num, tb_infection_rate, hiv_tb_infection_rate) %>%
            filter(tb_cleaning$year == 2019 & tb_cleaning$hiv_num >= 500) %>%
            replace(is.na(.), 0) %>%
            mutate(country = fct_reorder(country, hiv_tb_infection_rate))
            
hiv_graph <- droplevels(hiv_graph)
```
```r
g <- hiv_graph %>%
  select('country', 'tb_infection_rate', 'hiv_tb_infection_rate') %>%
  gather(key = 'type', value = 'percentage', tb_infection_rate, hiv_tb_infection_rate) %>%
  ggplot(aes(x = percentage, y = reorder(country, type = 'hiv_tb_infection_rate', percentage), color = type)) +
  facet_grid(hiv_graph$continent~., scales = "free_y", space = "free_y") + 
  geom_point() +
  ggtitle("TB Incident among Non_Hiv and Hiv Patient") +
  ylab("") +
  scale_fill_brewer(palette = "Spectral")
g
```

```{r}
hiv_graph <- tb_cleaning %>%
            select(iso3, year, continent, country, hiv_num, tb_infection_rate, hiv_tb_infection_rate) %>%
            filter(tb_cleaning$year == 2019 & tb_cleaning$hiv_num >= 500) %>%
            replace(is.na(.), 0) %>%
            mutate(country = fct_reorder(country, hiv_tb_infection_rate))
            
hiv_graph <- droplevels(hiv_graph)

```

```{r, fig.width=15, fig.height=20}
g <- hiv_graph %>%
  select('country', 'tb_infection_rate', 'hiv_tb_infection_rate') %>%
  gather(key = 'type', value = 'percentage', tb_infection_rate, hiv_tb_infection_rate) %>%
  ggplot(aes(x = percentage, y = reorder(country, type = 'hiv_tb_infection_rate', percentage), color = type)) +
  facet_grid(hiv_graph$continent~., scales = "free_y", space = "free_y") + 
  geom_point() +
  ggtitle("TB Incident among Non_Hiv and Hiv Patient") +
  ylab("") +
  scale_fill_brewer(palette = "Spectral")
g
```

## Map graph for TB Infection Rate
* In Africa, the southern reigon has a generally higher TB infection rate than the northern reigon. South-east Asia has a higher TB infection rate than other region in Asia. Southern Americas has a higher TB infection rate than Northern Americas.
```r 
fig <- plot_ly(tb_cleaning, type='choropleth', locations=tb_cleaning$iso3, z=tb_cleaning$tb_infection_rate, frame = ~year, text=tb_cleaning$country.x, colorscale="magma")

fig
```

```{r}
fig <- plot_ly(tb_cleaning, type='choropleth', locations=tb_cleaning$iso3, z=tb_cleaning$tb_infection_rate, frame = ~year, text=tb_cleaning$country, colorscale="magma")

fig
```


## Vaccination and TB Cases by Continent
* From this graph below, it seems that the vaccination does not help a lot and further analysis should be done.
```r
vaccine_tb_count <- vaccine_inc %>% 
  mutate(vaccination_count_million = (vaccination_rate/100) * (population/1000000)) %>%
  select(1:3,5:9) %>% 
  replace(is.na(.),0)
vaccine_tb_group <- vaccine_tb_count %>% 
  select(2,4,3,8) %>%
  group_by(year,continent) %>% 
  summarise(sum_inc_in_million=sum(c_newinc)/1000000,sum_vac_million=sum(vaccination_count_million),.groups='drop')

vaccine_tb_category <- vaccine_tb_group %>% 
  mutate(continent_vaccine = paste(continent,'vaccine',sep = '-'),continent_case = paste(continent,'Incidence',sep = '-'))
    
fig <- plot_ly(data=vaccine_tb_category, colors='Spectral')
fig <- fig %>% add_trace(x=~year, y=~sum_vac_million, color=~continent_vaccine, line = list(shape = 'linear', dash = 'dot'),
    mode = "lines+markers",text="Number of Vaccination",
    marker = list(symbol = "star_diamond", size = 5)
) 

ay <- list(
  tickfont = list(color = "black"),
  overlaying = "y",
  side = "right",
  title = "Number of Vaccination (in Million)")


fig <- fig %>% add_trace(
    x=~year, y=~sum_inc_in_million, color=~continent_case, mode = "lines+markers", yaxis = "y2", text="Number of Cases"
)

fig <- fig %>% layout(
  title = "TB cases and Vaccination by Continents", yaxis2 = ay,
  xaxis = list(title="Year"),
  yaxis = list(title="Number of TB (in Million)")
)%>%
  layout(
  plot_bgcolor='#BBBBBB',
  legend = list(x = 1.1, y = 0)
)

fig
```
```{r}
vaccine_tb_count <- vaccine_inc %>% 
  mutate(vaccination_count_million = (vaccination_rate/100) * (population/1000000)) %>%
  select(1:3,5:9) %>% 
  replace(is.na(.),0)
vaccine_tb_group <- vaccine_tb_count %>% 
  select(2,4,3,8) %>%
  group_by(year,continent) %>% 
  summarise(sum_inc_in_million=sum(c_newinc)/1000000,sum_vac_million=sum(vaccination_count_million),.groups='drop')

vaccine_tb_category <- vaccine_tb_group %>% 
  mutate(continent_vaccine = paste(continent,'vaccine',sep = '-'),continent_case = paste(continent,'Incidence',sep = '-'))
    
fig <- plot_ly(data=vaccine_tb_category, colors='Spectral')
fig <- fig %>% add_trace(x=~year, y=~sum_vac_million, color=~continent_vaccine, line = list(shape = 'linear', dash = 'dot'),
    mode = "lines+markers",text="Number of Vaccination",
    marker = list(symbol = "star_diamond", size = 5)
) 

ay <- list(
  tickfont = list(color = "black"),
  overlaying = "y",
  side = "right",
  title = "Number of Vaccination (in Million)")


fig <- fig %>% add_trace(
    x=~year, y=~sum_inc_in_million, color=~continent_case, mode = "lines+markers", yaxis = "y2", text="Number of Cases"
)

fig <- fig %>% layout(
  title = "TB cases and Vaccination by Continents", yaxis2 = ay,
  xaxis = list(title="Year"),
  yaxis = list(title="Number of TB (in Million)")
)%>%
  layout(
  plot_bgcolor='#BBBBBB',
  legend = list(x = 1.1, y = 0)
)

fig

```

## Vaccination Rate by Continent
* For the TB vaccination rate, Oceania and Africa have the highest variance. And the vaccination rate increases for all five continents from 1992 to 2021. From the line graph, Europe has a stead decrease of TB infection rate. The TB infection rate of Asia and Africa increases util 2008 and after than infection rate two continents has a decreasing trend. Infection rate of Americas does not change a lot among those years.
```r
fig1 <- plot_ly(data=vaccine_tb_rate, 
                x = ~vaccination_rate, 
                y=~continent,frame = ~year,
                colors = "Spectral",
                type='box',color=~continent) %>% 
        layout(plot_bgcolor='#BBBBBB',
               title = "Vaccination Rate by Continent",
               yaxis = list(title='Continent'),
               xaxis = list(range=c(0,100)),
               showlegend = FALSE)

fig2 <- vaccine_tb_rate %>% 
        select(continent, year, tb_infection_rate) %>% 
        replace(is.na(.), 0) %>% 
        group_by(continent, year) %>%
        summarize(tb_infection_rate = median(tb_infection_rate)) %>% 
        mutate(tb_infection_rate = tb_infection_rate*100) %>% 
        plot_ly(x = ~year, 
                y = ~tb_infection_rate,
                color = ~continent,
                mode = "lines+markers",
                colors = "Spectral") %>% 
        layout(plot_bgcolor='#BBBBBB',
               title = "Incidence Rate among Years by Continents",
               yaxis = list(ticksuffix = "%"),
               legend = list(orientation = 'h'))

fig <- subplot(fig1, fig2, nrows = 1, margin = 0.03) %>% 
      layout(plot_bgcolor='#BBBBBB', 
        title = "Vaccination Rate Box Plot & Median Infection Rate Among Continents",
       xaxis = list( 
         zerolinecolor = '#ffff', 
         zerolinewidth = 2, 
         gridcolor = 'ffff'), 
       yaxis = list( 
         zerolinecolor = '#ffff', 
         zerolinewidth = 2, 
         gridcolor = 'ffff'))
fig
```


```{r warning=FALSE}
fig1 <- plot_ly(data=vaccine_tb_rate, 
                x = ~vaccination_rate, 
                y=~continent,frame = ~year,
                colors = "Spectral",
                type='box',color=~continent) %>% 
        layout(plot_bgcolor='#BBBBBB',
               title = "Vaccination Rate by Continent",
               yaxis = list(title='Continent'),
               xaxis = list(range=c(0,100)),
               showlegend = FALSE)

fig2 <- vaccine_tb_rate %>% 
        select(continent, year, tb_infection_rate) %>% 
        replace(is.na(.), 0) %>% 
        group_by(continent, year) %>%
        summarize(tb_infection_rate = median(tb_infection_rate)) %>% 
        mutate(tb_infection_rate = tb_infection_rate*100) %>% 
        plot_ly(x = ~year, 
                y = ~tb_infection_rate,
                color = ~continent,
                mode = "lines+markers",
                colors = "Spectral") %>% 
        layout(plot_bgcolor='#BBBBBB',
               title = "Incidence Rate among Years by Continents",
               yaxis = list(ticksuffix = "%"),
               legend = list(orientation = 'h'))

fig <- subplot(fig1, fig2, nrows = 1, margin = 0.03) %>% 
      layout(plot_bgcolor='#BBBBBB', 
        title = "Vaccination Rate Box Plot & Median Infection Rate Among Continents",
       xaxis = list( 
         zerolinecolor = '#ffff', 
         zerolinewidth = 2, 
         gridcolor = 'ffff'), 
       yaxis = list( 
         zerolinecolor = '#ffff', 
         zerolinewidth = 2, 
         gridcolor = 'ffff'))
fig
```
## Map for vaccination rate
* The vaccination rate in Eastern Asia and Southern Africa increases. While, the rate for Southern Americas decrease greatly after 2015.
```r
fig <- plot_ly(vaccine_df, type='choropleth', locations=vaccine_df$iso3, z=vaccine_df$X2019,colorscale="Viridis",text=vaccine_df$country)
fig <- fig %>% colorbar(title = "Vaccine Rate")
fig <- fig %>% layout(
    title = "Vaccine Rate in 2019"
)
fig
```
```{r}
fig <- plot_ly(vaccine_pivoted, type='choropleth', locations=vaccine_pivoted$iso3, z=vaccine_pivoted$vaccination_rate,frame = ~year, colorscale="Viridis",text=vaccine_pivoted$country)
fig <- fig %>% colorbar(title = "Vaccine Rate")
fig <- fig %>% layout(
    title = "Vaccine Rate From 1992-2021"
)
fig
```


## Tree plot
* In 2019, India and China have the highest number of TB incidence and South Africa has the highest number of TB incidence in Africa.
```r
tree <- vaccine_inc %>% 
  filter(year == 2019) %>% 
  select(1,5,3,7) %>% 
  drop_na(.)
treemap(tree, 
        index=c("continent","iso3"),
        vSize = "c_newinc",
        vColor = "vaccination_rate",
        type='value',
        palette = 'Spectral',
        
        title = 'Number of incidence in 2019'
        )
```
```{r}
tree <- vaccine_inc %>% 
  filter(year == 2019) %>% 
  select(1,5,3,7) %>% 
  drop_na(.)
treemap(tree, 
        index=c("continent","iso3"),
        vSize = "c_newinc",
        vColor = "vaccination_rate",
        type='value',
        palette = 'Spectral',
        
        title = 'Number of incidence in 2019'
        )

```



